From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-09 papers/ACL2020/analysis.tex
example figure for annotations, verification, predictions

>>>>

\begin{figure}
	\centering
	\footnotesize
	\begin{tabular}{p{3.7cm}p{3.7cm}}
	\includegraphics[scale=.2]{images/556_1063956_seed_ambiguous.png} &
	\includegraphics[scale=.2]{images/2657_1069343_singleton_obj.png} 
	\\
	Entry-level: rug (21) &  animal (9)\\
	\midrule
	Same-object: carpet (4, 0.7) &  yak (3,0.8), buffalo (2,0.7) \\
	Error-box: chair (5, 0.5), floor (3, 0.5) & \\
	Error-visual:  & cow (6,0.5), ram (3,0.7), bull (2,0.7)\\
	\midrule
	FRCNN$_{\text{VG1600}}$: floor & animal\\
	FRCNN$_{\text{VG1600--VGMN}}$: rug & cow \\
	\end{tabular}
	\caption{Annotations, verification and predictions for 2 objects: name (number of annotations, adequacy rating)}
\end{figure}
